### 2021-03-08 text/draft.tex
machine indexing

@@

As explained above, for the prototype we will use the out

!! Explain how to implementation works.

In addition to the already used algorithms we should also try
https://ai.finto.fi/?locale=en

!! Somewhere here we talk about indexing based on title and/or abstract
and/or fulltext. Fulltext is not yet implemented. Some observations to
do so: - the link to the fulltext is constructed from the data fields
\texttt{offical\ url} and \texttt{documebts\ -\ main}, e.g.,
\texttt{https\ \ ://edoc.unibas.ch/79633/} + \texttt{1/} +
\texttt{2020\_18\_Informed\ by\ wet\ feet\_How\ do\ floods\ affect\ property\ prices.pdf}
to get
\texttt{https://edoc.unibas.ch/79633/1/2020\_18\_Informed\ by\ wet\ feet\_How\ do\ floods\ affect\ property\ prices.pdf}

@@

The construction of the derivative gold standard takes x steps:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Extract the keywords from the sample data set.\\
\item
  Clean the extracted keywords.
\item
  Reconcile the extracted keywords with\ldots{}
\end{enumerate}

@@

Combining these parameters, we really have 100 Annif configurations
whose performance we want to compare and assess: Annif project \(*\)
text base \(*\) maximum number of suggestions \(= 5 * 2 * 10 = 100\).
Each configuration has a unique ID (called ``marker'' in what follows)
constructed by the convention:
\texttt{\{project\_id\}-\{abstract\}-\{fulltext\}-\{n\}-\{threshold\}}
where \texttt{project\_id} is the Annif project, \texttt{abstract} and
\texttt{fulltext} are boolean variables, \texttt{n} is the maximum
number of suggestions per item, and \texttt{threshold} is a variable for
a threshold Annif score.

>>>>

Annif vocs that are available

@@

Machine indexing with Annif was implemented using the annif-client
Python library (see https://pypi.org/project/annif-client/). The desired
output is that every item in the Edoc sample data set is assigned
subject terms by all available Annif API projects (namely,
\texttt{yso-en}, \texttt{yso-maui-en}, \texttt{yso-bonsai-en},
\texttt{yso-fasttext-en}, \texttt{wikidata-en}) based on all available
text bases (title or title and abstract). In order to distinguish these
assignments, we use a unique ID (called ``marker'' in what follows) for
each Annif configuration. A marker is constructed by the convention:
\texttt{\{project\_id\}-\{abstract\}-\{fulltext\}-\{n\}-\{threshold\}},
where \texttt{project\_id} is the Annif project, \texttt{abstract} and
\texttt{fulltext} are boolean variables, \texttt{n} is the maximum
number of suggestions per item, and \texttt{threshold} is a variable for
a threshold Annif score.

In order to generate the ouput, we call
\texttt{Data.super\_enrich\_with\_annif}, thereby iteratively calling
\texttt{Data.enrich\_with\_annif} for all items in
\texttt{/files/sample/sample\_master.json} for all Annif projects. The
output is saved in \texttt{/indexed/} as \texttt{indexed\_master.json}.

@@

The construction of the derivative gold standard takes three steps:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Extract the keywords from the sample data set.
\item
  Clean the extracted keywords.
\item
  Reconcile the extracted keywords with.
\end{enumerate}

@@

Combining these parameters, we really have 100 Annif configurations
whose performance we want to compare and assess: Annif project \(*\)
text base \(*\) maximum number of suggestions \(= 5 * 2 * 10 = 100\).
Remember the convention for constructing the marker that identifies a
configuration (see \protect\hyperlink{annif}{section ``Annif''}):
\texttt{\{project\_id\}-\{abstract\}-\{fulltext\}-\{n\}-\{threshold\}}.
